Internship Summary: Mid-Term Review

### 2020-07-20 RapportStage/Rapport.tex
update sec 5.1

Different partitioning

$Y_{l0}$ vs $P_l(\cos(\theta))$

Size of the basis set

Strong coupling ???

@@

\begin{itemize}
\item Corriger les erreurs dans la biblio
\item tableau nrj uhf, citation spin density wave et charge density wave
\end{itemize}

>>>>

In this part, we will try to investigate how some parameters of $\bH(\lambda)$ influence the radius of convergence of the perturbation series. The radius of convergence is equal to the closest singularity to the origin of $E(\lambda)$. The exceptional points are simultaneous solution of \eqref{eq:PolChar} and \eqref{eq:DPolChar} so we solve this system to find their position.

\begin{equation}\label{eq:PolChar}
\text{det}[E-\bH(\lambda)]=0
\end{equation}

\begin{equation}\label{eq:DPolChar}
\pdv{E}\text{det}[E-\bH(\lambda)]=0
\end{equation}

We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis. \\

Puis on rajoute les 3 autres partitionnements \\

Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). Parler de la possibilité de la base strong coupling. \\

Différence RHF/UHF, Hamiltonien non-bloc diagonal, coefficients complexe pour R<3/2 \\

Influence de la taille de la base en RHF et UHF \\

@@

\begin{itemize}
\item Corriger les erreurs dans la biblio
\item citation spin density wave et charge density wave
\end{itemize}
